Towards Cloud Bursting for Extreme Scale Supercomputers

### 2014-06-14 paper/paper.tex
0613

\documentclass[JIP,draft]{ipsj}
\usepackage{graphicx}

@@

%1
\section{Introduction}
An increasing number of scientifical applications are now running on Supercomputer for high performance computing nodes, large bandwidth and low latency interconnection environment, also a great number of processors for high scalability.
High parallel application runs faster on Supercomputer for fully usage of computing resource.
However, it is usually difficult for a non-computer-scientist to write a parallel program, or re-write some existing applications into parallel version.
Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, casusing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
One solution is running several virtual machines on a single physical machine for increasing utilization, which is used in TSUBAME Supercomputer.
However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critial in summer and nearly half of computing nodes have be shutted down to reduce electricity consumation in the case of TSUBAME Supercomputer. 
Facing these problems, one solution will be federate supercomputer with public cloud.
By using pulic cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
Of cause, there will be many callenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.

%2
\section{Background}

%3
\section{I/O Bursting Buffer Overview}
An overview of cloud environment and I/O Burst Buffer Model is described in this section.

@@

%For security consideration and the fact that IPv4 addresses becomes rare,
All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each cloud, so topology is not specifid here, interconnection network performance is measured by throughput.
There are a constant number of public IP addresses can be assigned to some computing nodes.
There is a shared storage for date sharing inside cloud, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.

\subsection{I/O Bursting Buffer Archiecture}

\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{overview}
	\caption{overall illustrate of I/O Bursting Buffer Archiecture}
	\label{overview}
\end{figure}

@@

Arrows stand for network connection.
Orange arrows are innerconnection networks inside cloud, although two clouds used the same color for innerconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
Black arrows are Internet connections, since there are a few amount of public IP addresses avaliable, only I/O buffer nodes are connect to Internet, also the amount of avaliable public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud. 
Although nodes with private IP address can use route or other net device to connect to Internet, but consider about security problem, also using route will reduce concurrent data transfer rate, here we assume all nodes in cloud only connect to local private network except I/O buffer nodes which connect to both local network and Internet.

Circles stand for computing nodes, which are used for standard computation.
Here we assume all computing nodes can communicate with each other, and also I/O buffer nodes and shared storage in the same cloud environment.
Squares are I/O buffer nodes, these nodes are used for data transfer between clouds, and are assigned with both public and private IP addresses.
I/O buffer nodes can use the same machine or VM as computing nodes, or can use network optimized nodes for larger throughput, but it is not required here.
Cylinders are shared storages, which are used to store data used by computing nodes, .

@@

@@

There are many facts will affect throughput of Internet,

\subsection{data reading}

\begin{figure}[tb]
	\centering
	\includegraphics[width=8cm]{reading}
	\caption{data reading operation}
	\label{reading}
\end{figure}

When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splited into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assgined a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.

After transfering data from shared storage, a I/O buffer node in cloud 1 connects with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2, and transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.

>>>>

\documentclass[JIP,draft]{ipsj}
\usepackage{graphicx}
\usepackage{amsmath}

@@

%1
\section{Introduction}
An increasing number of scientific applications are now running on Supercomputer for high performance computing nodes, large bandwidth and low latency interconnection environment, also a great number of processors for high scalability.
High parallel application runs faster on Supercomputer for fully usage of computing resource.
However, it is usually difficult for a non-computer-scientist to write a parallel program, or re-write some existing applications into parallel version.
Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, causing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
One solution is running several virtual machines on a single physical machine for increasing utilization, which is used in TSUBAME Supercomputer.
However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shutted down to reduce electricity consumption in the case of TSUBAME Supercomputer.

Facing these problems, one solution will be federate supercomputer with public cloud.
By using public cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
Of cause, there will be many challenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
Since the biggest problem will be data transfer throughput between two clouds, this paper focuses on methodology of increasing throughput.

In order to increase data transfer throughput, we propose a I/O bursting buffer architecture that uses several nodes in each cloud as a I/O nodes to achieve high throughput concurrent data transferring, and a I/O bursting buffer model that uses to switch between I/O bursting buffer mode and direct connect mode.
Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
Also, public cloud usually charges for nodes usage, using I/O bursting buffer may reduce the computation time, but I/O nodes will be charged for money, we also provide a cost-based model, this model evaluate total cost with and without I/O nodes.

Our contribution can be summary as following:
\begin{itemize}
	\item An architecture of I/O bursting buffer for increasing data transfer throughput between two clouds.
	\item A throughput-based I/O bursting buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when federating two clouds, and a cost-based I/O bursting buffer model uses to reduce the total cost.
	%\item 
	\item a evaluation of i/o bursting buffer architecture and two models by using data taken from several benchmarks from tsubame supercomputer and AMAZON EC2 public cloud.
\end{itemize}
%2
\section{Background}

%3
\section{I/O Bursting Buffer Overview}
An overview of I/O Burst Buffer architecture and two operations: reading writing are described in this section.
Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment.

Reading operation describes operations when issues reading data from another cloud storage, and writing operation describes operation when issues writing data to another cloud storage.

Migration operation occurs when some nodes have to be shutted down in one cloud 
all jobs running on these nodes have to be backed up by using snapshot,

@@

%For security consideration and the fact that IPv4 addresses becomes rare,
All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each cloud, so topology is not specified here, interconnection network performance is measured by throughput.
There are a constant number of public IP addresses can be assigned to some computing nodes.
There is a shared storage for date sharing inside cloud, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.

\subsection{I/O Bursting Buffer Architecture}

\begin{figure}[tb]
	\centering
%	\includegraphics[width=6cm]{overview}
	\caption{overall illustrate of I/O Bursting Buffer Architecture}
	\label{overview}
\end{figure}

@@

Arrows stand for network connection.
Orange arrows are innerconnection networks inside cloud, although two clouds used the same color for innerconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
Black arrows are Internet connections, since there are a few amount of public IP addresses available, only I/O buffer nodes are connect to Internet, also the amount of available public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud. 
Although nodes with private IP address can use route or other net device to connect to Internet, but consider about security problem, also using route will reduce concurrent data transfer rate, here we assume all nodes in cloud only connect to local private network except I/O buffer nodes which connect to both local network and Internet.

Circles stand for computing nodes, which are used for standard computation.
Here we assume all computing nodes can communicate with each other, and also I/O buffer nodes and shared storage in the same cloud environment.
Squares are I/O buffer nodes, these nodes are used for data transfer between clouds, and are assigned with both public and private IP addresses.
I/O buffer nodes can use the same machine or VM as computing nodes, or can use network optimized nodes for larger throughput, but it is not required here.
Cylinders are shared storages, which are used to store data used by computing nodes, usually shared storage is consist of several nodes with a distributed filesystem and uses a better network, offers a large throughput.

%Since there is a big gap between cloud inside data transferring and accross two clouds in throughput, our goal is to fill the gap.

@@

\subsubsection{Data Reading}

\begin{figure}[tb]
	\centering
%	\includegraphics[width=8cm]{reading}
	\caption{data reading operation}
	\label{reading}
\end{figure}

When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splitted into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assgined a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.% I/O buffer nodes use a main index to refer to the data position in global data.

After transferring data from shared storage finished, I/O buffer nodes in cloud 1 will connect with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2,
%here a sub-index is used to refer to each piece's position, 
then transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.

When data transfer finished, I/O buffer nodes connect with all computation nodes which needs data, then transfer data to the corresponding position by using a index protocol described below, of cause all data transfer are done in parallel.

\subsubsection{Data Writing}

\begin{figure}[tb]
	\centering
%	\includegraphics[width=8cm]{writing}
	\caption{data writing operation}
	\label{writing}
\end{figure}

Data writing operation doing the opposite operation as reading operation.

When a computing node in cloud 2 issues data writing, output data will be first buffered by I/O server in that node.
After output finished, I/O server connects with all I/O buffer nodes in the same cloud, and split output data into the number of I/O buffer nodes, then send each piece of data to each I/O buffer nodes Simultaneously.

I/O buffer nodes then again split data into the number of I/O buffer nodes in cloud 1, like reading operation, here sub-index is used to refer to data position. and then start to transfer data concurrently.

Then I/O buffer nodes write data to storage in cloud 1.

\subsubsection{Index Protocol}

\begin{figure}[tb]
	\centering
%	\includegraphics
	\caption{index protocol}
	\label{index protocol}
\end{figure}

As Fig.~\ref{index protocol} shows, two indexs are used in this protocol: main index and sub-index.
There are two phases of data splitting in both reading and writing operation,

@@

\begin{figure}[tb]
	\centering
%	\includegraphics
	\caption{definition}
	\label{definition}
\end{figure}

Throughput-based Model and Cost-based Model will be described in this section.
All definitions used are described in Fig.~\ref{definition}:

\begin{itemize}
	\item Numbers of computing nodes are $c_1,c_2$, and numbers of I/O buffer nodes are $n_1, n_2$ respectively.
	\item $D_1(n_2)$ is throughput when $n_2$ I/O nodes in cloud 1 connect to storage in cloud 2 directly, similar to $D_1(n_2)$, $D_2(n_1)$ refers to throughput when $n_1$ I/O nodes in cloud 2 connect to storage in cloud 1 directly, here we assume only I/O nodes in each cloud have Internet connection.
	\item Since overall Internet throughput is affected by number of nodes involved in connection. $I(n_1,n_2)$ is used to refer to Internet throughput using $n_1,n_2$ I/O buffer nodes respectively.
	\item For interconnection network throughput, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in cloud 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in cloud 2 with $n_2$ I/O nodes.
	\item $M_1(n_1),M_2(n_2)$ are throughput of connection between storage and $n_1$ I/O nodes in cloud 1 and ,storage and $n_2$ I/O nodes in cloud 2.
	\item Cost for standard node in cloud 1 is defined as $C_1\_Money(T)$ for $T$ time usage and cost for node in cloud 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, here cost for I/O nodes is defined as $C_1\_High\_Money(T),C_2\_High\_Money(T)$ for $T$ time respectively.

\end{itemize}

\subsection{Throughput-based Model}
%There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
When I/O buffer nodes in cloud 2 connect to storage in cloud 1, there are two data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to storage in cloud 1, so throughput will be:

\begin{equation}
	\text{throughput}_{\text{direct}}=\min\{D_1(n_2),E_2(n_2)\} \label{throughput1}
\end{equation}

In the case of using I/O buffer nodes in both cloud, there are three data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to I/O buffer nodes in cloud 1, I/O buffer nodes in cloud 1 to storage in cloud 1, throughput will be:

\begin{equation}
	\text{throughput}_{\text{I/O buffer}}=\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} \label{throughput2}
\end{equation}

In this throughput-based model, these two throughput are evaluated, and a switch is based on these two values:

\begin{equation}
	\begin{cases}
		\text{throughput}_{\text{direct}} \geq \text{throughput}_{\text{I/O buffer}} & \text{use direct connection}\\
		\text{throughput}_{\text{direct}} < \text{throughput}_{\text{I/O buffer}} & \text{use I/O buffer}
	\end{cases}
\end{equation}

\subsection{Cost-based Model}
In the case of cost-based model, we consider
using \ref{throughput1},and \ref{throughput2} total time for transferring unit size of data can be compute as:

\begin{equation}
	\begin{cases}
		T_1=\frac{1}{\min\{D_1(n_2),E_2(n_2)\}} & \text{direct connection}\\
		T_2=\frac{1}{\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}} &\text{I/O buffer}
	\end{cases}
\end{equation}

here we compute cost by using $T_1,T_2$:
\begin{equation}
	\text{cost}_\text{direct}=c_2\times C_2\_Money(T_1)+n_2\times C_2\_High\_Money(T_1)
\end{equation}
\begin{align}
	\text{cost}_\text{I/O buffer}&=c_2\times C_2\_Money(T_2)\\\nonumber 
				     &+n_1\times C_1\_High\_Money(T_2)\\ \nonumber
				     &+n_2\times C_2\_High\_Money(T_2)
\end{align}
\subsection{Migration Model}
%\begin{equation}

%\end{eqaution}
\section{Evaluation}
